---
title: "607 Week 2"
author: "Benson"
date: "2/13/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup}
library(dplyr)
library(ggplot2)
```

## Six recent popular moviews survey

This is an analysis to understand which movie is favorite by my friends and family. I was doing this survey by asking my friends and family to rate the recent popular movies (Spider-man: No Way Home, Death on the Nile, Jackass forever, Scream, Marry Me, Moonfall).


```{r db}
#Prepare MySQL connection and connecting to Rstudio
library(RMySQL)

db_user <- 'root'
db_password <- 'abcd1234'
db_name <- 'movieDB'
db_table <- 'moviesurvey'
db_host <- '127.0.0.1'

myConnection <- dbConnect(MySQL(), user=db_user, password=db_password, host=db_host, dbname=db_name)


#check database
dbSendQuery(myConnection, 'DROP SCHEMA IF EXISTS `movieDB`;')
#create database
dbSendQuery(myConnection, 'CREATE SCHEMA `movieDB` ;')
#use database
dbSendQuery(myConnection, 'USE `movieDB` ;')

#check table 
dbSendQuery(myConnection, 'DROP TABLE IF EXISTS moviesurvey;')
#create table
dbSendQuery(myConnection, 'CREATE TABLE moviesurvey (movie varchar(255) NOT NULL,respondent_gender varchar(255) NOT NULL,respondent_relationship varchar(255) NOT NULL,respondent_age int NOT NULL,movie_rating int NOT NULL);')

#insert data
dbSendQuery(myConnection, "INSERT INTO moviesurvey
    (movie,respondent_gender,respondent_relationship,respondent_age,movie_rating)
VALUES
    ('SpiderMan:No Way Home','Male','Friend',31,5),
    ('SpiderMan:No Way Home','Male','Slibing',30,5),
    ('SpiderMan:No Way Home','Female','Friend',29,3),
    ('SpiderMan:No Way Home','Male','Slibing',18,4),
    ('SpiderMan:No Way Home','Female','Slibing',31,3),
    ('Death on the Nile','Male','Friend',31,3),
    ('Death on the Nile','Male','Slibing',30,4),
    ('Death on the Nile','Female','Friend',29,4),
    ('Death on the Nile','Male','Slibing',18,3),
    ('Death on the Nile','Female','Slibing',31,4),
    ('Jackass forever','Male','Friend',31,3),
    ('Jackass forever','Male','Slibing',30,4),
    ('Jackass forever','Female','Friend',29,4),
    ('Jackass forever','Male','Slibing',18,5),
    ('Jackass forever','Female','Slibing',31,2),
    ('Marry Me','Male','Friend',31,2),
    ('Marry Me','Male','Slibing',30,2),
    ('Marry Me','Female','Friend',29,5),
    ('Marry Me','Male','Slibing',18,2),
    ('Marry Me','Female','Slibing',31,4),
    ('Scream','Male','Friend',31,2),
    ('Scream','Male','Slibing',30,3),
    ('Scream','Female','Friend',29,4),
    ('Scream','Male','Slibing',18,5),
    ('Scream','Female','Slibing',31,4),
    ('Moonfall','Male','Friend',31,4),
    ('Moonfall','Male','Slibing',30,4),
    ('Moonfall','Female','Friend',29,1),
    ('Moonfall','Male','Slibing',18,5),
    ('Moonfall','Female','Slibing',31,2);
    ")


#Load the dataframe
query <- paste0("select * from ", db_table)
runQuery <- dbSendQuery(myConnection, query)
df <- fetch(runQuery, n=-1)
```

## Summary dataframe and data cleaning
```{r df}
# summary df
summary(df)

#data cleaning
df <- df %>% mutate(respondent_relationship = replace(respondent_relationship,respondent_relationship == "Slibing", "Sibling"))

unique(df$respondent_relationship)
```



## Analysis with ggplot
```{r analysis}


# average rating of each movie

ggplot(data = df)+
  aes(x=movie, y=movie_rating, color=movie)+
  ggtitle("Movie average rating")+
  geom_jitter()+
  geom_boxplot(size=1, alpha=0.5)+
  theme(plot.title=element_text(hjust=0.5))

print("All movies have the average rating 4 except movie Marry Me.")

ggplot(data = df) +
  aes(x = movie_rating, fill = movie) + 
  ggtitle("Movie rating")+
  geom_histogram(bins = 30) +
  facet_wrap(~movie, nrow = 3)

print("Both Spiderman and Jackass forever have the highest rating, and Spiderman has favorited.")

ggplot(data = df) +
  aes(y = movie_rating, fill = movie) +
  ggtitle("Movie rating by gender")+
  geom_histogram(bins = 30) +
  facet_wrap(~respondent_gender, nrow = 2)

print("My female sibling favor movie is Marry Me.")

ggplot(data = df) +
  aes(x = movie_rating, fill = respondent_relationship) +
  ggtitle("Movie rating by relation with me")+
  geom_histogram(bins = 30) +
  facet_wrap(~movie, nrow = 2)

print("My friends and siblings favor movie is Spiderman.")
```

## Summary
Based on my survey for the six movies, I found that females are more likely to watch Marry Me and males don't. However, this dataset is biased with low participation in the survey. 
Using an online survey platform like SurveyMonkey can help increase the number of participants. Also, people worldwide can easily access the survey thru online surveys. 
While increasing the number of participants can make this analysis more meaningful.

## Close Database Connection
```{r closedb}
#Close the db connection
dbDisconnect(myConnection)
```

